Research paper

### 2012-12-22 Research paper.tex
RP: Added societal relevance

% Ook lingusitic relevance: Abstracting fully lexicalised constructions
%Finding semantic subclasses in constructions: from time-expression to time-expression"
%Collapsing constructions with word disjunctions (\he/she/it") or part-of-speech tags
% Correlations with experimental findings
% Switch tasks, cloze tests, reaction times, ...

\subsection{For society}

@@

@@

\subsubsection{Machines translation improves communication between the world's communities}

%Bruggetje naar relevance for society

>>>>

Because Colibri's goals are not reached at the moment and there currently is no certainty about whether this will happen, Colibri's scientific relevance for now is relatively small; as described in the previous section, the already existing open source machine translation system MOSES has similar results. I should add, however, that the current state the project is in seems to be a fertile ground for breakthroughs in the future.

\subsection{For society} \label{soc}

Assuming such a breakthrough will indeed come, the relevance for society is a big one: by improving the quality of machine translation, one basically improves (1) to what extent someone can get information from a document written in a human language he or she does not master, and (2) to what extent people without a common language can communicate. As for the first point, a lot of the roughly 7000 languages in the world also have a written form. This means that, unless you know all of these languages, part of all information available can only be reached by translation. This can of course be done a translator, but that's a time-consuming and labour-intensive job, which forces us to concentrate on translating only the more important documents to the more important languages. With good machine translation, we can easily make available \emph{all} information available to everyone. The second point is perhaps even more important: if for two people there isn't a language they both speak, they have very little ways to communicate. In practice this means whole communities of people are excluded from the rest of the world, simply because they do not know the languages of the rest of the world. In highly educated societies this is of course less of a problem, as people can easily learn a new language as long as they are willing to do some effort, but foreign language education is not available in large parts of the world. If it manages to get good enough, machine translation might save the day here: by building 'linguistic bridges' between the world's communities, it creates the possibility for everyone on the world to communicate with everyone on the world. This means one is no longer limited to the community he or she was born, which may increase one's chances for a happy and succesful life seriously.

@@

Besides the general strength described in section \ref{soc}, Colibri has (at least) two more:

@@
